Qualitative Assessesment of Graph Neural Network Potentials for Phonon Properties of Shape Memory Alloys using Graph Neural Network Potentials

### 2024-02-04 src/tex/ms.tex
So annoying that the ms.tex, Snakefile, and showyourwork file need output fig name?.
Ahh I'm so impatient with naming, make sure to check figure namesgit add NiTi.Snakefile src/tex/ms.tex !

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Mutter_B2_StrainsPhononbandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Zhong_B2_StrainsPhononBandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Ko_B2_StrainsPhononBandstructure.png}
		\caption{ Phonon dispersion of B2 structure for the (top) EAM
			Mutter, (middle) EAM Zhong, and (bottom) 2NN-MEAM Ko potentials
			at different isotropic strains. The optical branches have been
			made more transparent to emphasis the behavior in the TA$_1$ and
			TA$_2$ branches. The color indicates direction from compressive
			to tensile strain. Note that the strain percent shown is with
			respect to isotropic changes (i.e. volume).  }
		\label{fig:mutter_zhong_ko_phonon_b2}
	\end{centering}
\end{figure}

@@

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_M3GNet_B2_StrainsPhononBandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_CHGNet_B2_StrainsPhononBandstructure.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_MACE_B2_StrainsPhononBandstructure.png}
		\caption{ Phonon dispersion of B2 structure for the (top) M3GNet,
			(middle) CHGNet, and (bottom) MACE potentials for different
			isotropic strains. Similar transcparency is used as done in
			\ref{fig:mutter_zhong_phonon_b2}.  }
		\label{fig:gnn_phonon_b2}
	\end{centering}
\end{figure}

>>>>

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Mutter_B2_StrainsPhononBandstructures.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Zhong_B2_StrainsPhononBandstructures.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_Ko_B2_StrainsPhononBandstructures.png}
		\caption{ Phonon dispersion of B2 structure for the (top) EAM
			Mutter, (middle) EAM Zhong, and (bottom) 2NN-MEAM Ko potentials
			at different isotropic strains. The optical branches have been
			made more transparent to emphasis the behavior in the TA$_1$ and
			TA$_2$ branches. The color indicates direction from compressive
			to tensile strain. Note that the strain percent shown is with
			respect to isotropic changes (i.e. volume).  }
		\label{fig:mutter_zhong_ko_phonon_b2}
	\end{centering}
\end{figure}

@@

\begin{figure}[!htp]
	\script{PlotPhonons.py}
	\begin{centering}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_M3GNet_B2_StrainsPhononBandstructures.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_CHGNet_B2_StrainsPhononBandstructures.png} \vspace{1mm}
		\includegraphics[width=0.5\linewidth]{figures/NiTi_MACE_B2_StrainsPhononBandstructures.png}
		\caption{ Phonon dispersion of B2 structure for the (top) M3GNet,
			(middle) CHGNet, and (bottom) MACE potentials for different
			isotropic strains. Similar transcparency is used as done in
			\ref{fig:mutter_zhong_phonon_b2}.  }
		\label{fig:gnn_phonon_b2}
	\end{centering}
\end{figure}
